Dependent Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-13 main.tex
Writing subsubsections.
Fill out definitions and theorems.

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{color}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\newcommand{\red}[1]{\textcolor{red}{ #1 }}
\newcommand{\blue}[1]{\textcolor{blue}{ #1 }}
\newcommand{\TW}{\triangleright}
\newcommand{\LTP}{$\lambda^{\triangleright\%}$}
\newcommand{\LMD}{$\lambda^{\textrm{MD}}$}
\newcommand{\LLF}{$\lambda^{\textrm{LF}}$}

\begin{document}
%
\title{Dependent Typed Multi-Stage Calculus\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Akira Kawata\inst{1} \and
Atsushi Igarashi\inst{2}\orcidID{0000-0002-5143-9764}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Graduate School of Informatics, Kyoto University, Kyoto, Japan\\
\email{akira@fos.kuis.kyoto-u.ac.jp} \and
\email{igarashi@kuis.kyoto-u.ac.jp}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}

@@

\blue{203 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
%
%
%
\section{Introduction}
\subsection{Dependent Types}
\subsection{Multi-Stage Calculus}
\subsection{Organaization of the Paper}
\section{Informal Overview of \LMD}
\subsection{\LLF}
\subsection{\LTP}
\section{Formal Definition of \LMD}
\subsection{Kinding Rules}
\subsection{Equivalence Rules}
\section{First Section}
\section{Related Work}
\section{Conclusions}

\subsection{A Subsection Sample}
Please note that the first paragraph of a section or subsection is
not indented. The first paragraph that follows a table, figure,
equation etc. does not need an indent, either.

Subsequent paragraphs, however, are indented.

\subsubsection{Sample Heading (Third Level)} Only two levels of
headings should be numbered. Lower level headings remain unnumbered;
they are formatted as run-in headings.

\paragraph{Sample Heading (Fourth Level)}
The contribution should contain no more than four levels of
headings. Table~\ref{tab1} gives a summary of all heading levels.

\begin{table}
\caption{Table captions should be placed above the
tables.}\label{tab1}
\begin{tabular}{|l|l|l|}
\hline
Heading level &  Example & Font size and style\\
\hline
Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
\hline
\end{tabular}
\end{table}

\noindent Displayed equations are centered and set on a separate
line.
\begin{equation}
x + y = z
\end{equation}
Please try to avoid rasterized images for line-art diagrams and
schemas. Whenever possible, use vector graphics instead (see
Fig.~\ref{fig1}).

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
\caption{A figure caption is always placed below the illustration.
Please note that short captions are centered, while long ones are
justified by the macro package automatically.} \label{fig1}
\end{figure}

\begin{theorem}
This is a sample theorem. The run-in heading is set in bold, while
the following text appears in italics. Definitions, lemmas,
propositions, and corollaries are styled the same way.
\end{theorem}
%
% the environments 'definition', 'lemma', 'proposition', 'corollary',
% 'remark', and 'example' are defined in the LLNCS documentclass as well.
%
\begin{proof}
Proofs, examples, and remarks have the initial word in italics,
while the following text appears in normal font.
\end{proof}
For citations of references, we prefer the use of square brackets
and consecutive numbers. Citations using labels or the author/year
convention are also acceptable. The following bibliography provides
a sample reference list with entries for journal
articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
and a homepage~\cite{ref_url1}. Multiple citations are grouped
\cite{ref_article1,ref_lncs1,ref_book1},
\cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
\bibitem{ref_article1}
Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

\bibitem{ref_lncs1}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\bibitem{ref_book1}
Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
Location (1999)

\bibitem{ref_proc1}
Author, A.-B.: Contribution title. In: 9th International Proceedings
on Proceedings, pp. 1--2. Publisher, Location (2010)

\bibitem{ref_url1}
LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
Oct 2017
\end{thebibliography}
\end{document}

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bcprules, proof}
\usepackage{fancybox}
\usepackage{mathtools}
\usepackage{float}
\usepackage[truedimen,margin=15truemm]{geometry}
\usepackage{xparse}
\usepackage{ebproof}
\usepackage{lscape}
\usepackage{mdframed}

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\newcommand{\red}[1]{\textcolor{red}{ #1 }}
\newcommand{\blue}[1]{\textcolor{blue}{ #1 }}

\newcommand{\LTP}{$\lambda^{\triangleright\%}$}
\newcommand{\LMD}{$\lambda^{\textrm{MD}}$}
\newcommand{\LLF}{$\lambda^{\textrm{LF}}$}

\newcommand{\G}{\Gamma}
\newcommand{\D}{\Delta}
\newcommand{\V}{\vdash}
\newcommand{\VT}{\vdash\hspace{-.50em}\raisebox{0.28em}{\tiny{$\TB$}}}
\newcommand{\iskind}{\text{\ kind}}
\newcommand{\TW}{\triangleright}
\newcommand{\TWL}{\triangleleft}
\newcommand{\F}{\forall}
\newcommand{\TB}{\blacktriangleright}
\newcommand{\TBL}{\blacktriangleleft}
\newcommand{\E}{\equiv}
\newcommand{\FV}{\text{FV}}
\newcommand{\FTV}{\text{FTV}}

\newcommand{\WStar}{\textsc{W-Star}}
\newcommand{\WAbs}{\textsc{W-Abs}}
\newcommand{\WCsp}{\textsc{W-Csp}}
\newcommand{\WApp}{\textsc{W-App}}
\newcommand{\WTW}{\textsc{W-$\TW$}}

\newcommand{\KVar}{\textsc{K-Var}}
\newcommand{\KAbs}{\textsc{K-Abs}}
\newcommand{\KApp}{\textsc{K-App}}
\newcommand{\KConv}{\textsc{K-Conv}}
\newcommand{\KTW}{\textsc{K-$\TW$}}
\newcommand{\KTWL}{\textsc{K-$\TWL$}}
\newcommand{\KGen}{\textsc{K-Gen}}
\newcommand{\KCsp}{\textsc{K-Csp}}

\newcommand{\TVar}{\textsc{T-Var}}
\newcommand{\TAbs}{\textsc{T-Abs}}
\newcommand{\TApp}{\textsc{T-App}}
\newcommand{\TConv}{\textsc{T-Conv}}
\newcommand{\TTB}{\textsc{T-$\TB$}}
\newcommand{\TTBL}{\textsc{T-$\TBL$}}
\newcommand{\TGen}{\textsc{T-Gen}}
\newcommand{\TIns}{\textsc{T-Ins}}
\newcommand{\TCsp}{\textsc{T-Csp}}

\newcommand{\QKAbs}{\textsc{QK-Abs}}
\newcommand{\QKCsp}{\textsc{QK-Csp}}
\newcommand{\QKRefl}{\textsc{QK-Refl}}
\newcommand{\QKSym}{\textsc{QK-Sym}}
\newcommand{\QKTrans}{\textsc{QK-Trans}}

\newcommand{\QTAbs}{\textsc{QT-Abs}}
\newcommand{\QTApp}{\textsc{QT-App}}
\newcommand{\QTTW}{\textsc{QT-$\TW$}}
\newcommand{\QTGen}{\textsc{QT-Gen}}
\newcommand{\QTCsp}{\textsc{QT-Csp}}
\newcommand{\QTRefl}{\textsc{QT-Refl}}
\newcommand{\QTSym}{\textsc{QT-Sym}}
\newcommand{\QTTrans}{\textsc{QT-Trans}}

\newcommand{\QAbs}{\textsc{Q-Abs}}
\newcommand{\QApp}{\textsc{Q-App}}
\newcommand{\QTB}{\textsc{Q-$\TB$}}
\newcommand{\QTBL}{\textsc{Q-$\TBL$}}
\newcommand{\QGen}{\textsc{Q-Gen}}
\newcommand{\QIns}{\textsc{Q-Ins}}
\newcommand{\QCsp}{\textsc{Q-Csp}}
\newcommand{\QRefl}{\textsc{Q-Refl}}
\newcommand{\QSym}{\textsc{Q-Sym}}
\newcommand{\QTrans}{\textsc{Q-Trans}}
\newcommand{\QBeta}{\textsc{Q-$\beta$}}
\newcommand{\QEta}{\textsc{Q-$\eta$}}
\newcommand{\QTBLTB}{\textsc{Q-$\TBL\TB$}}
\newcommand{\QLambda}{\textsc{Q-$\Lambda$}}
\newcommand{\QPercent}{\textsc{Q-\%}}

\newcommand{\ID}[1]{\infer[]{#1}{\vdots}}
\newcommand{\MD}[1]{\mathcal{D}_#1}

\begin{document}
%
\title{Dependent Typed Multi-Stage Calculus\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Akira Kawata\inst{1} \and
Atsushi Igarashi\inst{2}\orcidID{0000-0002-5143-9764}}
%
\authorrunning{A. Kawata, A. Igarashi}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Graduate School of Informatics, Kyoto University, Kyoto, Japan\\
\email{akira@fos.kuis.kyoto-u.ac.jp} \and
\email{igarashi@kuis.kyoto-u.ac.jp}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}

@@

\blue{203 words. The abstract should briefly summarize the contents of the paper in 150--250 words.}
%
%
%
\section{Introduction}
\subsection{Multi-Stage Calculus}
\subsubsection{Introduction to Multi-Stage Calculus}
\subsubsection{Application to Performance Imporving}
\subsection{Dependent Types}
\subsubsection{Introduction to Dependent Types}
\subsubsection{Application to Omitting Boundary Checking}
\subsection{Organaization of the Paper}

\section{Informal Overview of \LMD}
\subsection{\LLF}
\subsection{\LTP}

\section{Formal Definition of \LMD}
\subsection{Syntax}

\begin{align*}
    \textrm{Terms} && M,N,L,O,P & ::= x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M 
    \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M\\ 
    \textrm{Types} && \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} M \mid \F\alpha.\tau \\
    \textrm{Kinds} && K,J,I,H,G & ::= * \mid \Pi x:\tau.K\\
    \textrm{Contexts} && \Gamma & ::= \phi \mid 
    \Gamma,x:\tau@A\ (x\not\in\textrm{FV}(\G)) \mid 
    \Gamma,X::K@A\ (X\not\in \textrm{FV}(\G))\\
    \textrm{Transition variables} && & \alpha,\beta,\gamma,... \\
    \textrm{Transition} && & A,B,C,... \\
    \textrm{Variables} && & x,y,z,... \\
    \textrm{Type variables} && & X,Y,Z,... \\
\end{align*}

\subsection{Reduction}

\begin{definition}[Reduction]
\begin{align*}
    & (\lambda x:\tau.M) N \longrightarrow_\beta M[x \mapsto N] \\
    % & (\Pi x:\tau.\sigma) M \longrightarrow_\gamma \sigma[x \mapsto M] \\
    & \TBL_\alpha (\TB_\alpha M)\longrightarrow_\blacklozenge M \\
    & (\Lambda \alpha.M) \epsilon \longrightarrow_\Lambda M[\alpha \mapsto \epsilon]
\end{align*}
And take a minimum compatible relationship on terms.
\end{definition}

\subsection{Type System}
\subsubsection{Kinding Rules}
\subsubsection{Equivalence Rules}

\subsection{Properties}

\begin{theorem}[Substituition Lemma for Variables of Terms, Types or Kinds and Their Equivalence]
    \begin{flalign*}
        \text{If\ } \G,z:\xi@B \V M:\tau@A \text{\ and\ } \G\V P:\xi@B
        &\text{\ then\ } \G\V M[z \mapsto P]:\tau[z \mapsto P]@A.&\\
        \text{If\ } \G,z:\xi@B \V \tau::K@A \text{\ and\ } \G\V P:\xi@B
        &\text{\ then\ } \G\V \tau[z \mapsto P]::K[z \mapsto P]@A.&\\
        \text{If\ } \G,z:\xi@B \V K\iskind@A \text{\ and\ } \G\V P:\xi@B
        &\text{\ then\ } \G\V K[z \mapsto P] \iskind @A.&\\
        \text{If\ } \G,z:\xi@B \V M\E N : \tau@A \text{\ and\ } \G\V P:\xi@B
        &\text{\ then\ } \G\V M[z \mapsto P]\E N[z \mapsto P] : \tau[z \mapsto P]@A.&\\
        \text{If\ } \G,z:\xi@B \V \tau\E \sigma : K@A \text{\ and\ } \G\V P:\xi@B
        &\text{\ then\ } \G\V \tau[z \mapsto P]\E \sigma[z \mapsto P] : K[z \mapsto P]@A.&\\
        \text{If\ } \G,z:\xi@B \V K\E J@A \text{\ and\ } \G\V P:\xi@B
        &\text{\ then\ } \G\V K[z \mapsto P]\E J[z \mapsto P]@A.&
    \end{flalign*}    
\end{theorem}

\begin{theorem}[Stage Substituition Lemma for Variables of Terms, Types or Kinds and Their Equivalence]
    \begin{flalign*}
        \text{If\ } \G \V M:\tau@A
        &\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]:\tau[\beta \mapsto \epsilon]@A[\beta \mapsto \epsilon].&\\
        \text{If\ } \G \V \tau::K@A
        &\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]::K[\beta \mapsto \epsilon]@A[\beta \mapsto \epsilon].&\\
        \text{If\ } \G \V K\iskind@A
        &\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon] \iskind@A[\beta \mapsto \epsilon].&\\
        \text{If\ } \G \V M\E N : \tau@A
        &\text{\ then\ } \G[\beta \mapsto \epsilon]\V M[\beta \mapsto \epsilon]\E N[\beta \mapsto \epsilon] : \tau[\beta \mapsto \epsilon] @A[\beta \mapsto \epsilon].&\\
        \text{If\ } \G \V \tau\E \sigma : K@A
        &\text{\ then\ } \G[\beta \mapsto \epsilon]\V \tau[\beta \mapsto \epsilon]\E \sigma[\beta \mapsto \epsilon] : K[\beta \mapsto \epsilon]@A[\beta \mapsto \epsilon].&\\
        \text{If\ } \G \V K\E J@A
        &\text{\ then\ } \G[\beta \mapsto \epsilon]\V K[\beta \mapsto \epsilon]\E J[\beta \mapsto \epsilon]@A[\beta \mapsto \epsilon].&
    \end{flalign*}
\end{theorem}

\begin{theorem}[Preservation for term on $\beta$ reduction]
    If $\G\V M:\tau@A$ and $M \longrightarrow_{\beta} M'$, then $\G\V M':\tau@A$\\
\end{theorem}

\begin{theorem}[Preservation for term on $\TBL\TB$ reduction]
    If $\G\V M:\tau@A$ and $M\longrightarrow_\blacklozenge N$, then $\G\V N:\tau@A$\\
\end{theorem}

\begin{theorem}[Preservation for term on $\Lambda$ reduction]
    If $\G\V M:\tau@A$ and $M \longrightarrow_{\Lambda} N$, then $\G\V N:\tau@A$.
\end{theorem}

\begin{theorem}[Strong Normalization]
    If $\G\V^A t:T$ then there is no infinite sequence of terms $(t_i)_{i\ge1}$ and $t_i \longrightarrow_{\beta, \TBL \TB,\Lambda} t_{i+1}$ for $i\ge 1$
\end{theorem}

\begin{theorem}[Confluence(Church-Rosser Property)]
    Define $M \longrightarrow N$ as $M \longrightarrow_{\beta} N$ or $M\longrightarrow_\blacklozenge N$ or  $M \longrightarrow_{\Lambda} N$.\\
    For any term $M$, if $M \longrightarrow^* N$ and $M \longrightarrow^* L$,
    there exists $O$ that satisfies $N \longrightarrow^* O$ and $L \longrightarrow^* O$.
\end{theorem}

\begin{definition}[Values]
$A \neq \epsilon$\\
\begin{align*}
    \textrm{Values} && v^\epsilon \in V^\epsilon & ::= \lambda x:\tau.M \mid\ \TB_\alpha v^\alpha \mid \Lambda\alpha.v^\epsilon & \\
                    && v^A \in V^A & ::= x \mid \lambda x:\tau.v^A \mid v^A\ v^A \mid\ \TB_\alpha v^{A\alpha} 
                                           \mid \Lambda\alpha.v^A \mid v^A\ \epsilon &\\
                                    &&& \quad\   \mid\ \TBL_\alpha v^{A'} (\text{if } A'\alpha = A \text{ and } A' \neq \epsilon) & \\
                                    &&& \quad\   \mid \%_\alpha v^{A'} (\text{if } A'\alpha = A) & \\
    \textrm{Redexes} && R^\epsilon & ::= (\lambda x:\tau.M)\ v^\epsilon \mid (\Lambda\alpha.v^\epsilon)\ \epsilon & \\
                     && R^\alpha & ::=\ \TBL_\alpha \TB_\alpha M & \\
\end{align*}
\end{definition}

\begin{definition}[Reduction]
    $ M \longrightarrow M'$ iff \\
    $ M \longrightarrow_\Lambda M' $, $ M \longrightarrow_\blacklozenge M' $ or $ M \longrightarrow_\beta M' $.
\end{definition}

\begin{theorem}[Progress]
    If $x:\tau@\epsilon \notin \G$ and $\G \V M : \tau @ A$ then $ M \in V^A $ or $\exists M'$ such that $M \longrightarrow M'$.
\end{theorem}

\section{Related Work}

\section{Conclusions}

% \section{First Section}
% \subsection{A Subsection Sample}
% Please note that the first paragraph of a section or subsection is
% not indented. The first paragraph that follows a table, figure,
% equation etc. does not need an indent, either.
% 
% Subsequent paragraphs, however, are indented.
% 
% \subsubsection{Sample Heading (Third Level)} Only two levels of
% headings should be numbered. Lower level headings remain unnumbered;
% they are formatted as run-in headings.
% 
% \paragraph{Sample Heading (Fourth Level)}
% The contribution should contain no more than four levels of
% headings. Table~\ref{tab1} gives a summary of all heading levels.
% 
% \begin{table}
% \caption{Table captions should be placed above the
% tables.}\label{tab1}
% \begin{tabular}{|l|l|l|}
% \hline
% Heading level &  Example & Font size and style\\
% \hline
% Title (centered) &  {\Large\bfseries Lecture Notes} & 14 point, bold\\
% 1st-level heading &  {\large\bfseries 1 Introduction} & 12 point, bold\\
% 2nd-level heading & {\bfseries 2.1 Printing Area} & 10 point, bold\\
% 3rd-level heading & {\bfseries Run-in Heading in Bold.} Text follows & 10 point, bold\\
% 4th-level heading & {\itshape Lowest Level Heading.} Text follows & 10 point, italic\\
% \hline
% \end{tabular}
% \end{table}
% 
% 
% \noindent Displayed equations are centered and set on a separate
% line.
% \begin{equation}
% x + y = z
% \end{equation}
% Please try to avoid rasterized images for line-art diagrams and
% schemas. Whenever possible, use vector graphics instead (see
% Fig.~\ref{fig1}).
% 
% \begin{figure}
% \includegraphics[width=\textwidth]{fig1.eps}
% \caption{A figure caption is always placed below the illustration.
% Please note that short captions are centered, while long ones are
% justified by the macro package automatically.} \label{fig1}
% \end{figure}
% 
% \begin{theorem}
% This is a sample theorem. The run-in heading is set in bold, while
% the following text appears in italics. Definitions, lemmas,
% propositions, and corollaries are styled the same way.
% \end{theorem}
% %
% % the environments 'definition', 'lemma', 'proposition', 'corollary',
% % 'remark', and 'example' are defined in the LLNCS documentclass as well.
% %
% \begin{proof}
% Proofs, examples, and remarks have the initial word in italics,
% while the following text appears in normal font.
% \end{proof}
% For citations of references, we prefer the use of square brackets
% and consecutive numbers. Citations using labels or the author/year
% convention are also acceptable. The following bibliography provides
% a sample reference list with entries for journal
% articles~\cite{ref_article1}, an LNCS chapter~\cite{ref_lncs1}, a
% book~\cite{ref_book1}, proceedings without editors~\cite{ref_proc1},
% and a homepage~\cite{ref_url1}. Multiple citations are grouped
% \cite{ref_article1,ref_lncs1,ref_book1},
% \cite{ref_article1,ref_book1,ref_proc1,ref_url1}.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{main}
%
% \begin{thebibliography}{8}
% \bibitem{ref_article1}
% Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)
% 
% \bibitem{ref_lncs1}
% Author, F., Author, S.: Title of a proceedings paper. In: Editor,
% F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
% Springer, Heidelberg (2016). \doi{10.10007/1234567890}
% 
% \bibitem{ref_book1}
% Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
% Location (1999)
% 
% \bibitem{ref_proc1}
% Author, A.-B.: Contribution title. In: 9th International Proceedings
% on Proceedings, pp. 1--2. Publisher, Location (2010)
% 
% \bibitem{ref_url1}
% LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
% Oct 2017
% \end{thebibliography}
\end{document}
